Data_visualization

### 2018-09-11 Rmd/Data_visualization_common_names.Rmd
trait csv
Adding density plots of stigma area

@@

>>>>

\newpage

###POLLEN OVULE RATIO. TOTAL POLLEN PER FLOWER DIVIDED BY NUMBER OF OVULES

@@

\newpage

###STIGMA AREA

```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}

t_stigma_area <- read.csv("Data/t_stigma_area.csv")
t_stigma_area_brassicaceae <- read.csv("Data/t_stigma_area_brassicaceae.csv")
t_stigma_area_solanaceae <- read.csv("Data/t_stigma_area_solanaceae.csv")
t_stigma_area_convolvulaceae <- read.csv("Data/t_stigma_area_convolvulaceae.csv")

theme_set(theme_gray())
a <- ggplot(t_stigma_area_brassicaceae, aes(x = um, fill = species_common)) +
  geom_density(alpha = 0.7) +
  theme(legend.position = c(0.8, 0.8))

b <- ggplot(t_stigma_area_solanaceae, aes(x = um, fill = species_common)) +
  geom_density(alpha = 0.7) +
  theme(legend.position = c(0.8, 0.8))

cowplot::plot_grid(a,b, labels = "AUTO")
```

```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}

t_stigma_area <- read.csv("Data/t_stigma_area.csv")
t_stigma_area_brassicaceae <- read.csv("Data/t_stigma_area_brassicaceae.csv")
t_stigma_area_solanaceae <- read.csv("Data/t_stigma_area_solanaceae.csv")
t_stigma_area_convolvulaceae <- read.csv("Data/t_stigma_area_convolvulaceae.csv")

theme_set(theme_gray())
a <- ggplot(t_stigma_area, aes(x = um, fill = species_common)) +
  geom_density(alpha = 0.7) +
  theme(legend.position = c(0.8, 0.8))

cowplot::plot_grid(a, labels = "AUTO")

###All Area per family

theme_set(theme_gray())
a <- ggplot(t_stigma_area, aes(x = um, fill = family)) +
  geom_density(alpha = 0.7) +
  theme(legend.position = c(0.8, 0.8))

cowplot::plot_grid(a, labels = "AUTO")
